Baseline centering problem

### 2018-12-20 paper/tangotd.tex

We should find a way to initialize $Z$ so that $Z\approx \Id$ at time
$0$, namely $Z(s,s)=1/\rho(s)$, although starting with $Z(s,s)=1$ should be
quite fine. (Small initializations of $Z$ are safer.) $Z>0$ (unless we
work with $\gamma=1$ and relative stuff), so the parameterization should
reflect that. Indeed the Newton iteration is unstable with negative
values.

@@

Newton has a potential to be numerically less stable: first because of
the $(1+\eta)$ factor which makes $Z$ quickly grow when it's small (until
the $-Z^2$ kicks in), then because of the $-Z^2$ factors which can be
problematic when $Z$ is large. Small enough learning rates should be
stable. (TODO NOT TRUE: even in 1d, Newton is unstable if initialized to
a negative number, for any learning rate. Stable only in some
neighborhood of the true solution, but then, the stochastic noise might
produce divergence...)

>>>>

Initialization: A first idea would be to start with paths from $s$ to
$s$, namely, initialize
$Z$ so that $Z\approx \Id$ at time
$0$, namely $Z(s,s)=1/\rho(s)$, although starting with $Z(s,s)=1$ should be
quite fine. (Small initializations of $Z$ are safer.) $Z>0$ (unless we
work with $\gamma=1$ and relative stuff), so the parameterization should
reflect that. Indeed the Newton iteration is unstable with negative
values.

Another initialization might be $Z(s_1,s_2)\approx \frac{1}{1-\gamma}$
for every pair $s_1,s_2$. Indeed, on-policy, $Z$ is the density with
respect to the invariant distribution $\mu$, and for $\gamma$ close to
$1$, $Z$ will be approximately $\frac{1}{1-\gamma}$ plus a smaller function (see
below). Note that $Z(s_1,s_2)=\frac{1}{1-\gamma}$ is an exact solution of
the middle Bellman equation (as is $Z=0$), but it is a repulsive fixed
point, I think, so initializing to $\frac{1}{1-\gamma}$ plus noise should
converge to the true solution. Initializing there should have the
advantage of starting close to reasonable values.

@@

Newton has a potential to be numerically less stable: first because of
the $(1+\eta)$ factor which makes $Z$ quickly grow when it's small (until
the $-Z^2$ kicks in), then because of the $-Z^2$ factors which can be
problematic when $Z$ is large. Small enough learning rates should be
stable. (TODO NOT TRUE: even in 1d, Newton is unstable if initialized to
a negative number, for any learning rate. Stable only in some
neighborhood of the true solution, but then, the stochastic noise might
produce divergence... this is potentially a serious issue)
